### 2022-01-12 doc/src/AdvPLIC.tex
For Adv. PLIC, allow clearing level-sensitive intrs. with MSI delivery

\item
The pending bit is cleared whenever the rectified input value is low,
or when the interrupt is forwarded by MSI.
The pending bit cannot be cleared by a write to an \z{in\_clrip}
register or to \z{clripnum}.

>>>>

\item
The pending bit is cleared whenever the rectified input value is low,
when the interrupt is forwarded by MSI, or by a relevant write
to an \z{in\_clrip} register or to \z{clripnum}.
